### 2018-06-16 Project log/multiple_outcomes_project_log.Rmd
Log new sims

>>>>

\subsection{2018-6-XXX re-running Freedman simulations }

Re-running Freedman simulations after catching bug in prop.corr function that was causing too few of the X-Y pairs to be correlated. Also reduced $B$ from 2000 to 1000 and sim.reps from 1000 to 500.

Results do look a bit less stable with these reduced values. When everything is done running, maybe try running an additional 1000 sim reps of the strong null scenarios (1-4) to see if that causes all the methods to hit 5% power exactly. If not, then maybe this suggests we really do need B=2000 (and should put that in paper).
